### 2013-05-16 mcmc.tex
note to self
notes to self

@@

>>>>

...Return here to the proposal distribution, which exists for most methods...

@@

...Priors: If you describe your priors in one parameterization but
then perform sampling in a different space, it is easy to make
mistakes.  For example: Flat prior in amplitude and phase, sample in
$A\,\cos\phi$ and $A\,\sin\phi$.  There are many ways to do this
wrong.
